Model_additionalAlts

### 2015-11-30 models/Model_additionalAlts.Rmd
basic functionlity and output for subjective 'addtional' scalars - do the funky results for liked_lovedpalatable_delicious (when we have something like 0.1, 0.1, 0.5, 0.1, 0.9) suggest that we need more than one other additional scalar?

---
title: "Model_additionalAlts"
author: "BPeloquin"
date: "November 25, 2015"
output: html_document
---
```{r include=FALSE}
rm(list=ls())

@@

# good_excellent
combos = data.frame(c(0, 0, 1, 0, 0),
                    c(0, 0.05, 0.9, 0.05, 0),
                    c(0, 0.1, 0.8, 0.1, 0),
                    c(0, 0.2, 0.6, 0.2, 0.9),
                    c(0, 0.2, 0.6, 0.2, 1),
                    c(0.05, 0.2, 0.6, 0.2, 0.05),
                    c(0, 0.25, 0.5, 0.25, 0))  
focus_alts("good_excellent", combos=combos, alpha = 4, normalize=T)
focus_alts("good_excellent", combos=combos, alpha = 8, normalize=F)

# some_all
combos = data.frame(c(0, 1, 0, 0, 0),
                    c(0.05, 2, 0.05, 0.05, 0.05),
                    c(0.1, 0.8, 0.1, 0, 0),
                    c(0.2, 0.6, 0.2, 0, 0),
                    c(0.25, 0.5, 0.25, 0, 0))
focus_alts("some_all", combos=combos, alpha=4, normalize=T)
focus_alts("some_all", combos=combos, alpha=8, normalize=F)

@@

# palatable_delicious
combos = data.frame(rep(0.1, 5),
                    c(0.05, 2, 0.05, 0.05, 0.05),
                    c(0.05, 1, 0.05, 0.05, 0.05),
                    c(0.05, 0.05, 0.05, 0.9, 0.1),
                    c(0.05, 0.8, 0.05, 0.9, 0.05),
                    c(0.05, 0.7, 0.05, 0.9, 0.05),
                    c(0.05, 0.6, 0.05, 0.05, 0.05),
                    c(0.05, 0.5, 0.05, 0.05, 0.05),
                    c(0.1, 0.8, 0.1, 0.1, 0.1))
focus_alts("palatable_delicious", combos=combos, alpha=4, normalize=T)
focus_alts("palatable_delicious", combos=combos, alpha=8, normalize=F)
```

Focus on `some_all`:
```{r}
ge.subset = data.full[data.full$scale == "some_all", ]
ge.subset[ge.subset$degree == "mid", "speaker.p"] = c(0, 1, 0, 0, 0)
head(ge.subset, n = 20)
target.scalars = c("hi1", "low1")

# Run model
m1 = ge.subset %>%
  do(run.full(., alpha = 8, addMid = T))
cor(m1$pred, m1$listener.p)

qplot(stars, listener.p, col=degree, 
      data=m1,
      ylab="Posterior p(rating | word)") + 
  geom_line(aes(y = pred), lty = 4)

m1 = m1[m1$degree %in% target.scalars, ]
cor(m1$pred, m1$listener.p)

combos = data.frame(c(0, 0, 1, 0, 0),
                    c(0, 0.05, 0.9, 0.05, 0),
                    c(0, 0.1, 0.8, 0.1, 0),
                    c(0, 0.2, 0.6, 0.2, 0),
                    c(0, 0.25, 0.5, 0.25, 0))
colnames(combos) = LETTERS[1:length(colnames(combos))]
cors = c()
for (i in 1:ncol(combos)) {
  print(i)
  ge.subset = data.full[data.full$scale == "good_excellent", ]
  ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
  target.scalars = c("hi1", "hi2")
  # Run model
  m1 = ge.subset %>%
    do(run.full(., alpha = 8, addMid = T))
  m1 = m1[m1$degree %in% target.scalars, ]
  cors[i] = cor(m1$pred, m1$listener.p)  
}
cors 
```

>>>>

---
title: "Model_additionalAlts"
author: "BPeloquin"
date: "November 25, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 3
---
```{r include=FALSE}
rm(list=ls())

@@

# good_excellent
combos = data.frame(c(0, 0, 1, 0, 0),
                    c(0, 0.05, 0.9, 0.05, 0),
                    c(0, 0.1, 0.8, 0.1, 0),
                    c(0, 0.2, 0.2, 0.2, 0.9),
                    c(0, 0.2, 0.6, 0.2, 1),
                    c(0, 0.2, 0.6, 0.3, 0.2),
                    c(0, 0.2, 0.6, 0.3, 0.3),
                    c(0, 0.2, 0.6, 0.5, 0.4),
                    c(0, 0.2, 0.6, 0.5, 0.5),
                    c(0, 0.2, 0.6, 0.6, 0.4),
                    c(0.05, 0.2, 0.6, 0.2, 0.05),
                    c(0, 0.25, 0.5, 0.25, 0))  
focus_alts("good_excellent", combos=combos, alpha = 1, normalize=T)
focus_alts("good_excellent", combos=combos, alpha = 8, normalize=F)

# some_all
combos = data.frame(c(0, 1, 0, 0, 0),
                    c(0.05, 2, 0.05, 0.05, 0.05),
                    c(0.2, 0.9, 0.2, 0.1, 0.1),
                    c(0.2, 0.9, 0.2, 0.1, 0),
                    c(0.1, 0.9, 0.1, 0, 0),
                    c(0.1, 0.8, 0.1, 0, 0),
                    c(0.2, 0.6, 0.2, 0, 0),
                    c(0.25, 0.5, 0.25, 0, 0))
focus_alts("some_all", combos=combos, alpha=4, normalize=T)
focus_alts("some_all", combos=combos, alpha=8, normalize=F)

@@

# palatable_delicious
combos = data.frame(rep(0.1, 5),
                    c(0.05, 2, 0.05, 0.05, 0.05),
                    c(0.05, 1, 0.05, 0.05, 0.05),
                    c(0.05, 0.05, 0.05, 0.9, 0.1),
                    c(0.05, 0.05, 0.05, 0.9, 0.05),
                    c(0.05, 0.7, 0.05, 0.5, 0.05),
                    c(0.05, 0.6, 0.05, 0.05, 0.05),
                    c(0.05, 0.5, 0.05, 0.05, 0.05),
                    c(0.1, 0.8, 0.1, 0.1, 0.1))
focus_alts("palatable_delicious", combos=combos, alpha=4, normalize=T)
focus_alts("palatable_delicious", combos=combos, alpha=8, normalize=F)
```
